---
title: "TheKidsBiostatsTemplate"
subtitle: "A biostatistics report template"
author:
  name: "J Smith, Biostatistician"
  affiliation:
  - "The Kids Research Institute Australia, Perth, WA, Australia"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  docx:
    reference-doc: thekids_quarto_template.docx
    toc: false
    toc-depth: 3
    toc-title: Contents
    number-sections: true
    number-depth: 1
    highlight-style: github
    fig-dpi: 300
editor_options: 
  chunk_output_type: console
execute:
  echo: false
  warning: false
  message: false
  error: true
mainfont: Barlow
fig-align: center
fig-format: png
---

```{r init, include = F}
library(targets)
library(jtools)
library(biometrics)

models <- tar_read(models)
plots <- tar_read(plots)


```

## Introduction

### Project Summary

A blurb describing the project, which team or individual is conducting the research

### Research Question

A succinct, specific research question to be answered in this report.

::: callout-important
This must be confirmed with the researcher
:::

## Data Summary

Tables, explanatory plots, etc to examine the data prior to analysis.

## Analysis

### Linear Model

```{r echo = T}
summ(models$model1)
```

## Supplementary Material

### Plots

```{r echo = F}
plots$model1
```


